%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}
%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\usepackage[colorlinks]{hyperref}

\begin{document}

\name{Laura Chapman}
\tagline{Associate Software Engineer}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{lc.chapman5@gmail.com }
      \phone{9146409318}
    \linkedin{linkedin.com/in/laurachapman/}
 \homepage{laurachapman.github.io}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}
% \statement{Highly motivated and detail-oriented software engineer with excellent communication skills. Looking for a role in a fast-paced environment solving cool problems with smart people.}

%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}


%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
% \cvsection[page1sidebar]{Experience}
\begin{fullwidth}
\cvsection{Experience}
\cvevent{Software Engineer II}{Google}{June 2021 -- Present}{Washington, DC}
\begin{itemize}
\item Working on Economic Security team within Google Search.
\item Building search features for government services and food assistance. 
\end{itemize}
\vspace{6pt}
\cvevent{Associate Software Engineer}{Capital One}{August 2020 -- June 2021}{Boston, MA}
\begin{itemize}
\item Spearheaded development of major new feature on a treasury management application in Scala/Typescript/React.
\item Built utilities to increase team's efficiency, migrated projects to new AWS account, and contributed to documentation.
\item Led demonstrations and discussions with business partners and tech teams. 
\end{itemize}
\vspace{6pt}
\cvevent{Teaching Fellow}{Harvard Department of Computer Science}{September 2019 -- August 2020}{Cambridge, MA}
\begin{itemize}
\item Courses: CS171: Visualization, CS10: Elements of Data Science, and CS1: Introduction to Programming with Python.
\item Taught section, assisted in labs and lectures, graded assignments, mentored students and held office hours. 
\item Earned Harvard Certificate of Distinction in Teaching. 
\end{itemize}
\vspace{6pt}
\cvevent{Software Engineering Intern}{Capital One}{June 2019 -- August 2019}{New York, NY}
\begin{itemize}
\item Created an interactive network visualization using JavaScript/D3 for an internal web application. 
\item Constructed data pipeline, optimized performance, and built visualization code into a flexible library. 
\item Named a "super performer" by manager and received return offer.
\end{itemize}
\vspace{6pt}
\cvsection{Skills}
\textbf{\color{accent}Languages/libraries:}
\cvtag{Scala}
\cvtag{React}
\cvtag{JS/TS}
\cvtag{Python}
\cvtag{HTML}
\cvtag{CSS}
\cvtag{SQL}
\cvtag{D3.js}
\cvtag{OCaml}
\cvtag{C}
\cvtag{ZIO}
\vspace{3pt}

\textbf{\color{accent}Technologies:}
\cvtag{AWS}
\cvtag{Jenkins}
\cvtag{Git}
\cvtag{Docker}
\cvtag{Jira}
\cvtag{Kanban}
\medskip

\cvsection{Personal projects}
\begin{itemize}
\item \textfb{\color{accent}Solving \textit{Are You the One?} With Functional Scala}- applying dynamic programming/constraint satisfaction to a dating show
\item \textfb{\color{accent}Ranked Choice Voting with Harvard Chicken Dishes}- visually exploring ranked choice voting with chicken preferences
\item \textfb{\color{accent}Computer generated art and Instagram bot}- creating content and building a following semi-automatically
\end{itemize}
For links and more, visit \textbf{\color{accent}laurachapman.github.com/nerdy}
\medskip

\cvsection{Education}
\cvevent{Bachelor's in Computer Science, Minor in Physics, 3.78 GPA}{Harvard University}{2016 -- 2020}{Cambridge, MA}{\textfb{\color{accent}Coursework: }Compilers, Theoretical Computer Science, Data Structures and Algorithms, Systems Programming and Machine Organization, Visualization, Introduction to Artificial Intelligence with Python}

\medskip
\end{fullwidth}

\end{document}
